### 2017-04-03 paper/evaluation.tex
added missing content
adjustments on rq3

To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
parallelization settings enabled by default identified in \numRQC{}
and compared their time cost with sequential execution. We are
interested in measuring the execution speedup (if any) when the
parallelization settings are activated. It is important to mention
that we ignored the remaining \Fix{??} subjects identified in
Section~\ref{sec:rqC-2} because it would be impractical to execute
each subject on specific conditions to measure the impact of
parallelization.

To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
analyzed the \numProjectsPar{} subjects looking for the parallelism 
configuration inside the \pomf{} of each module. To run the subjects
sequentially, we manually modified the Maven Surefire configuration
from the \numPomMatched{} identified before to not run in parallel.

@@

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
\Luis{rework this... $\rightarrow$}To reduce the number of build files
to inspect, we consider only \pomf{} files that contain
\CodeIn{plugin} tags with a child tag \CodeIn{artifactId} with the
value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
node. This mining step, however, is not sound as a matching project may not 
indicate a project with a valid configuration for running tests in parallel.

>>>>

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default, and
compared their time cost with sequential execution. We are interested
in measuring the execution speedup (if any) when the parallelization
settings are activated.

%% To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
%% parallelization settings enabled by default identified in \numRQC{}
%% and compared their time cost with sequential execution. We are
%% interested in measuring the execution speedup (if any) when the
%% parallelization settings are activated. It is important to mention
%% that we ignored the remaining \Fix{??} subjects identified in
%% Section~\ref{sec:rqC-2} because it would be impractical to execute
%% each subject on specific conditions to measure the impact of
%% parallelization.

To enforce sequential execution, we analyzed the \numProjectsPar{}
subjects looking for the parallelism configuration inside the \pomf{} 
of each module. To run the subjects sequentially, we manually modified 
the Maven Surefire configuration in order to force the subjects to
execute tests in sequential mode.

@@

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
To reduce the number of build files
to inspect, we consider only \pomf{} files that contain
\CodeIn{plugin} tags with a child tag \CodeIn{artifactId} with the
value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
node. Figure~\ref{fig:surefire-configuration} shows an example of
configuration node mined. This mining step, however, is not sound as a matching project may not 
indicate a project with a valid configuration for running tests in parallel.
